---
title             : "Normative information and meat consumption"
shorttitle        : "The effect of dynamic norms"
author: 
  - name          : "Alaa AlDoh"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "a.aldoh@sussex.ac.uk"
affiliation:
  - id            : "1"
    institution   : "University of Sussex"
keywords          : "dynamic norm, sustainability"
wordcount         : "X"
output: 
  bookdown::html_document2:
    theme: journal
    toc: true
    toc_depth: 2
    toc_float: true
    highlight: pygments
    code_folding: hide
---

```{r setup, include = FALSE}
source("03_exploratory.R")
# or sys.source("your-script.R", envir = knitr::knit_global())

set.seed(42)
knitr::opts_chunk$set(echo=F, warning = F, message = F)
#options(knitr.table.format = "latex")
```


## Exploratory Analyses

### 3. Does dynamic norm (versus static or no norm) information increase participants’ positive attitude, intentions, and expectations to reduce their meat consumption?
    
```{r SEM, results="asis"}
h3.table %>%
  kable(format = "html", caption = "Posterior results for simple model (H3)", escape = F) %>% 
  add_header_above(c(" " = 1, "Model 1: Uninformative priors" = 5, "Model 2: Informative priors" = 5, "Model 3: Informative priors" = 5)) %>%
  kable_styling()
```

### 4. How does age interact with norm condition to influence dependent variables? 
```{r Interaction, results="asis"}
interact.table %>% 
  kable(format = "html", caption = "Posterior results for multi-sample analysis by age (H4)", row.names = F, escape = F) %>%
  add_header_above(c(" " = 1, "Model 1: Uninformative priors" = 5, "Model 2: Informative priors" = 5, "Model 3: Informative priors" = 5)) %>%  
  kable_styling() %>%
  pack_rows("Older", 1, 4) %>%
  pack_rows("Younger", 5, 8)
```

### 5. How do demographic factors such as age, gender, and political position predict primary dependent variables relating to meat consumption? 

```{r full SEM, results='asis'}
h5.table %>% 
  kable(format = "html", caption = "Posterior results for full model (H5)", row.names = F, escape = F) %>%
  kable_styling() %>%
  add_header_above(c(" " = 1, "Model 1: Uninformative priors" = 5, "Model 2: Informative priors" = 5, "Model 3: Informative priors" = 5)) %>%
  pack_rows("Interest", 1, 4) %>%
  pack_rows("Attitudes", 5, 8) %>%
  pack_rows("Intentions", 9, 12) %>%
  pack_rows("Expectations", 13, 16)
```
